P.~T.~Bauman, R.~H.~Stogner, ``GRINS: A Multiphysics Framework based on
the libMesh Finite Element Library", SIAM Journal on Scientific
Computing, 2016, in press.

\blankline

T. M. van Opstal, P. T. Bauman, S. Prudhomme, E. H. van Brummelen,
``Goal-oriented model adaptivity for viscous incompressible flows'',
Computational Mechanics, 55(6), 1181--1190, 2015

\blankline

E.~E.~Prudencio, P.~T.~Bauman, D.~Faghihi,
K.~Ravi-Chandar, J.~T.~Oden,
``A computational framework for dynamic data-driven material damage
control, based on Bayesian inference and model selection'',
Int. J. Numerical Methods Engng., 102(3-4), 379--403, 2015

\blankline

E.~E.~Prudencio, P.~T.~Bauman, S.~V.~Williams, D.~Faghihi,
K.~Ravi-Chandar, J.~T.~Oden,
``Real-time inference of stochastic damage in composite materials'',
Composites Part B: Engineering, 67, 209--219, 2014

\blankline

%
%\begin{outerlist}
%\item [1.]
B.~S.~Kirk, R.~H.~Stogner, P.~T.~Bauman, and T.~A.~Oliver,
``Modeling Hypersonic Entry with the Fully-Implicit Navier-Stokes (\texttt{FIN-S})
stabilized finite element solver'', Computers \& Fluids, 92(20),
281--292, 2014

\blankline

J.~T.~Oden, E.~E.~Prudencio, P.~T.~Bauman,
``Virtual model validation of complex multiscale systems:
Applications to nonlinear elastostatics",
Comput. Methods Appl. Mech. Engrg., 266, 162--184, 2013

\blankline

N. Malaya, K. C. Estacio-Hiroms, R. H. Stogner, K. W. Schulz, P.~T.~Bauman,
G. F. Carey,
``MASA: A Library for Verification Using Manufactured and Analytical Solutions",
Engineering with Computers, 29(4), 487--496, 2013

\blankline

P.~T.~Bauman, R. Stogner, G. F. Carey, K. W. Schulz, R. Upadhyay, A. Maurente, ``Loose-Coupling Algorithm for Simulating
Hypersonic Flows with Radiation and Ablation", AIAA Journal of
Spacecraft and Rockets, 48(1), 71--80, 2011

\blankline

S. Prudhomme, L. Chamoin, H. Ben Dhia, P.~T.~Bauman, ``An adaptive
strategy for the control of modeling error in two-dimensional
atomic-to-continuum coupling simulations", Comput. Methods
Appl. Mech. Engrg., 198, 1887--1901, 2009

\blankline

P.~T.~Bauman, J. T. Oden, S. Prudhomme, ``Adaptive Multiscale Modeling
of Polymeric Materials: Arlequin Coupling and Goals Algorithms'',
Comput. Methods Appl. Mech. Engrg., 198, 799--818, 2009

\blankline

S. Prudhomme, H. Ben Dhia, P.~T.~Bauman, N. Elkhodja, J. T. Oden,
``Computational Analysis of Modeling Error for the Coupling of
Particle and Continuum Models by the Arlequin Method'',
Comput. Methods Appl. Mech. Engrg., 197(41-42), 3399--3409, 2008


\blankline

%\item[2.]
P.~T.~Bauman, H. Ben Dhia, N. Elkhodja, J. T. Oden, S. Prudhomme, ``On
the Application of the Arlequin Method to the Coupling of Particle and
Continuum Models'', Computational Mechanics, 42(4), 511--530, 2008

\blankline


D. L. Littlefield, P.~T.~Bauman, A. Molineux, ``Analysis of formation
of the Odessa crater'', Int. J. Impact Engrg., 34(12), 1953 -- 1961,
2007

\blankline

%\item[3.]
S. Prudhomme, P.~T.~Bauman, J. T. Oden, ``Error Control for Molecular
Statics Problems'', Int. J. Multiscale Comp. Eng., 4, 647 -- 662,
2006

\blankline

J. T. Oden, S. Prudhomme, A. Romkes, P.~T.~Bauman,``Multiscale
Modeling of Physical Phenomena: Adaptive Control of Models'', SIAM
J. Sci. Comp., 28, 2359 -- 2389, 2006

\blankline

J. T. Oden, S. Prudhomme, P.~Bauman, ``On the Extension of
Goal-Oriented Error Estimation and Hierarchical Modeling to Discrete
Lattice Models'', Comput. Methods Appl. Mech. Engrg., 194, 3668 --
3688, 2005

%\end{outerlist}


%==================================================================
% END OF FILE
%==================================================================
