R.~H.~Stogner, P.~T.~Bauman,
``Open-Source, Multi-Physics Finite Element Analysis Using LibMesh and GRINS'',
SIAM Conference on Parallel Processing, Portland, OR, Feb. 18--21, 2014

\blankline

V.~Carey, P.~T.~Bauman,
``Goal-Oriented Error Estimation and Adaptivity for the Time-Dependent Low-Mach Navier-Stokes Equations'',
MAFELAP 2013, Brunel University, Uxbridge, England, June 11--14, 2013

\blankline

P.~T.~Bauman,
``Error Estimation and Adaptive Modeling fo Viscous Incompressible Flows'',
MAFELAP 2013, Brunel University, Uxbridge, England, June 11--14, 2013

\blankline

P.~T.~Bauman,
``Determination of Nitridation Reaction Parameters Using Bayesian Inference'',
SIAM Conference on Computational Science and Engineering, Boston, MA, Feb. 25 -- Mar. 1, 2013

\blankline

P. T. Bauman, R. Moser,
``Data Reduction Modeling of a Graphite Nitridation Experiment", 
American Physical Society Division of Fluid Dynamics Meeting, San Diego, CA, Nov. 18--20, 2012.

\blankline

P. T. Bauman,  J. Jagodzinski, B. S. Kirk,
``Calibration of Thermocouple Gauges for Inferring Heat Flux through Statistical Inversion", USNCCM 11,
Minneapolis, MN, July 25--29, 2011.

\blankline

P. T. Bauman, J. Jagodzinski, B. S. Kirk,
``Statistical Calibration of Thermocouple Gauges Used for Inferring Heat Flux", 42nd AIAA Thermophysics
Conference, Honolulu HI, June 27--30, 2011.

\blankline

P.~T.~Bauman, M.~Panesi,
``Data Reduction Modeling and Experimental Uncertainty'',
PSAAP V\&V UQ Workshop, Austin, TX, July 7--9, 2010

\blankline


R. Moser, P. T. Bauman,
``Multiphysics Coupling Efforts within the PECOS Center", 
3rd Annual AFOSR/NASA/SNL Ablation Workshop, Austin, TX, March 24--25, 2010.

\blankline

P. T. Bauman, R. Stogner, G. F. Carey, K. W. Schulz, R. Updadhyay, A. Maurente,
``Multiphysics Coupling for Reentry flows",
48th AIAA Aerospace Sciences Meeting, Orlando, FL,  Jan. 4--7, 2010, AIAA Paper 2010-1462.

\blankline

P. T. Bauman, J. T. Oden, S. Prudhomme,
``Goal-Oriented Error Estimation and Adaptive Modeling of Coupled Particle and Continuum Models", 
MAFELAP 2009, Brunel University, Uxbridge, England, June 9--12, 2009.

\blankline

P. T. Bauman, S. Prudhomme, J. T. Oden,
``Adaptive Multiscale Modeling of Polymeric Materials used in Semiconductor Manufacturing", 
Nanotech 2009, Houston, TX, May 3--7, 2009.

\blankline

P. T. Bauman, J. Bass, J. T. Oden, S. Prudhomme,
``Adaptive Multiscale Modeling of Polymers with Arlequin Coupling'',
USNCCM 9, San Francisco, CA, July 23 -- 26, 2007.

\blankline

P. T. Bauman,
``Adaptive Multiscale Modeling of Polymeric Materials'',
Computational Science Graduate Fellowship Annual Fellows' Conference, Washington, D. C., June 19 -- 21, 2007.

\blankline

J. T. Oden, P. T. Bauman, S. Prudhomme, J. M. Bass,
``Adaptive Multi-Scale Modeling: Goals Algorithms for Adaptive Error Control'',
17th US Army Symposium on Solid Mechanics, Baltimore, MD, April 2-5, 2007.

\blankline

P. T. Bauman, S. Prudhomme, J. T. Oden,
``Application of Goal-Oriented Adaptivity to Multiscale Models in Molecular Dynamics'',
WCCM 7, Los Angeles, CA, July 16 -- 22, 2006.

\blankline

J. T. Oden, P. T. Bauman, S. Prudhomme,
``Estimation and Control of Modeling Error in Multi-Scale Simulation'',
Conference on Adaptive Model Reduction in PDE Constrained Optimization,
Rice University, Houston, TX, May 17 -- 19, 2006.

\blankline

P. Bauman, S. Prudhomme, and J. T. Oden,
``Application of Goal-Oriented Adaptive Modeling to Problems in Molecular Statics'',
USNCCM 8, Austin, TX, July 25 -- 27, 2005.

\blankline 

S. Prudhomme, P. Bauman, and J. T. Oden,
``Reliability of Atomistic-Continuum Modeling Simulations for Problems in Molecular Statics'',
ICCN 2005 Proceedings (Fifth International Conference on Computational Nanoscience and Nanotechnology),
Anaheim, CA, May 8 -- 12, 2005.

\blankline

D. L. Littlefield, P. T. Bauman,
``Deformation of fluted rods subjected to severe lateral loads'',
13th U.S. Army TARDEC Ground Vehicle Survivability Symposium, Monterey, CA, April 9 - 11, 2002.
